Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-08-10 tex/revised_manuscript.tex
Final edits 1st revision
figure names

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_amptyl}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.

@@

			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]). The indication of ``Sphaeralcea hastula A. Gray'' is not a valid name and appears to be a misspelling of \textit{Sphaeralcea hastulata}.

@@

%M. ampullaceus
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure1.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure2.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure3.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure4.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:ampullaceus_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure5.jpg}
	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
	\label{fig:ampullaceus_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure6.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
	\label{fig:ampullaceus_lamina}
\end{figure}

%M. franko
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure7.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure8.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure9.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure10.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:franko_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure11.jpg}
	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
	\label{fig:franko_maxilla}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure12.jpg}
	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
	\label{fig:franko_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure13.jpg}
	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:franko_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure14.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:franko_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure15.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
	\label{fig:franko_aedeagus}
\end{figure}

%M. sculptilis
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure16.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure17.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure18.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure19.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:sculptilis_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure20.jpg}
	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:sculptilis_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure21.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:sculptilis_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure22.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
	\label{fig:sculptilis_aedeagus}
\end{figure}

%M. tylotos
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure23.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure24.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure25.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure26.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:tylotos_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure27.jpg}
	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
	\label{fig:tylotos_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure28.jpg}
	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:tylotos_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure29.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:tylotos_lamina}
\end{figure}

%phylogeny
\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.85\textwidth]{figure30.png}
	\end{sideways}
	\caption{\textbf{Preferred phylogeny -- character transitions and support.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80). Characters 9, 27, 39, 45 - 47, 49, and 51 are mapped under ACCTRAN optimization; all others are unambiguously optimized. Black squares indicate non-homoplasious character state changes, whereas white squares indicate homoplasious character state changes. The numbers above and below the squares represent character numbers and states, respectively. Bremer support (upper value) and relative fit difference (lower value) values can be found at the left ends of the branches. A ``*'' symbol at the right end of a branch indicates Bootstrap support greater than 0.95.}
	\label{fig:tree1}
\end{figure}

%phylogeny
\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.85\textwidth]{figure31.png}
	\end{sideways}
	\caption{\textbf{Preferred phylogeny -- clade concept labels.} Topology and species-level taxonomic concept labels as in Fig.~\ref{fig:tree1}. Clade concept labels, numbered 1-20, are consistently generated by using the alphabetically first epithet in each of the bifurcating sister clades. This method safeguards the clade concept labels against changes due simply to reorientation of leaves. Bold-font square brackets indicate new [JF2018] labels. See also \textbf{\nameref{sec:alignments}}.}
	\label{fig:tree2}
\end{figure}

%RCC-5 alignment visualizations
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure32.png}
	\caption{\textbf{Intensional RCC--5 alignment of the rank-only classifications of \textit{Minyomerus} [JF2018]/[JF2015].} See also \citet{jansen2015} and \textbf{Supplemental Information SI2}. Taxonomic concept labels such as \textit{Minymerus microps} [JF2015] are abbreviated as "2015.Minyomerus\_microps". Relaxation of the coverage constraint is indicated with the prefix "nc\_" (no coverage). Congruent concept regions (T\textsubscript{2} and T\textsubscript{1}) are shown as grey rectangles, concepts regions unique to the later taxonomy (T\textsubscript{2}) are shown as green rectangles, and concept regions unique to the earlier taxonomy (T\textsubscript{1}) are shown as yellow octagons. Articulations of inverse proper inclusion $(<)$ and overlap $(><)$, where present, are also shown.}
	\label{fig:align1}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure33.png}
	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- whole-concept resolution with overlap.} See also \textbf{Supplemental Information SI3}. Seven overlapping articulations are inferred. For further discussion, see the \textbf{\nameref{sec:alignments}} section.}
	\label{fig:align2}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure34.png}
	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- split-concept resolution.} See also \textbf{Supplemental Information SI4}. The seven overlapping articulations of the alignment displayed Fig.~\ref{fig:align2} are resolved into their constituent split regions. That is, if regions A and B overlap, the three resulting split regions are labeled A\textbackslash b ("A, \emph{not} b"), A*B ("A \emph{and} B"), and B\textbackslash a ("B, \emph{not} a"). Five split-concept regions can \emph{only} be named using this convention, and are salmon-colored in the alignment visualization.}
	\label{fig:align3}
\end{figure}

%distribution maps
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure35.png}
	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
	\label{fig:map_summary}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure36.png}
	\caption{\textbf{Distributions of \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018], as indicated in the legend.}
	\label{fig:map_amptyl}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure37.png}
	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
	\label{fig:map_franko}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.85\textwidth]{figure38.png}
		\end{sideways}
	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
	\label{fig:map_sculptilis}
\end{figure}
\end{document}

>>>>

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.

@@

			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]).
			The indication of ``Sphaeralcea hastula A. Gray'' is not a valid name and appears to be a misspelling of \textit{Sphaeralcea hastulata} [non-focal].

@@

\newpage
%RCC-5 alignment visualizations
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure1.png}
	\caption{\textbf{Intensional RCC--5 alignment of the rank-only classifications of \textit{Minyomerus} [JF2018]/[JF2015].} See also \citet{jansen2015} and \textbf{Supplemental Information SI2}. Taxonomic concept labels such as \textit{Minymerus microps} [JF2015] are abbreviated as "2015.Minyomerus\_microps". Relaxation of the coverage constraint is indicated with the prefix "nc\_" (no coverage). Congruent concept regions (T\textsubscript{2} and T\textsubscript{1}) are shown as grey rectangles, concepts regions unique to the later taxonomy (T\textsubscript{2}) are shown as green rectangles, and concept regions unique to the earlier taxonomy (T\textsubscript{1}) are shown as yellow octagons. Articulations of inverse proper inclusion $(<)$ and overlap $(><)$, where present, are also shown.}
	\label{fig:align1}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure2.png}
	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- whole-concept resolution with overlap.} See also \textbf{Supplemental Information SI3}. Seven overlapping articulations are inferred. For further discussion, see the \textbf{\nameref{sec:alignments}} section.}
	\label{fig:align2}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure3.png}
	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- split-concept resolution.} See also \textbf{Supplemental Information SI4}. The seven overlapping articulations of the alignment displayed Fig.~\ref{fig:align2} are resolved into their constituent split regions. That is, if regions A and B overlap, the three resulting split regions are labeled A\textbackslash b ("A, \emph{not} b"), A*B ("A \emph{and} B"), and B\textbackslash a ("B, \emph{not} a"). Five split-concept regions can \emph{only} be named using this convention, and are salmon-colored in the alignment visualization.}
	\label{fig:align3}
\end{figure}

%distribution maps
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure4.png}
	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
	\label{fig:map_summary}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure5.png}
	\caption{\textbf{Distributions of \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. ampullaceus} [JF2018] and \textit{M. tylotos} [JF2018], as indicated in the legend.}
	\label{fig:map_amptyl}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure6.png}
	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
	\label{fig:map_franko}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.85\textwidth]{figure7.png}
		\end{sideways}
	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
	\label{fig:map_sculptilis}
\end{figure}

%M. ampullaceus
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure8.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure9.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure10.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure11.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:ampullaceus_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure12.jpg}
	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
	\label{fig:ampullaceus_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure13.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
	\label{fig:ampullaceus_lamina}
\end{figure}

%M. franko
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure14.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure15.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure16.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure17.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:franko_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure18.jpg}
	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
	\label{fig:franko_maxilla}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure19.jpg}
	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
	\label{fig:franko_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure20.jpg}
	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:franko_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure21.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:franko_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure22.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
	\label{fig:franko_aedeagus}
\end{figure}

%M. sculptilis
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure23.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure24.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure25.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure26.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:sculptilis_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure27.jpg}
	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:sculptilis_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure28.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:sculptilis_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure29.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
	\label{fig:sculptilis_aedeagus}
\end{figure}

%M. tylotos
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure30.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure31.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure32.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure33.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:tylotos_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure34.jpg}
	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
	\label{fig:tylotos_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure35.jpg}
	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:tylotos_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure36.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:tylotos_lamina}
\end{figure}

%phylogeny
\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.85\textwidth]{figure37.png}
	\end{sideways}
	\caption{\textbf{Preferred phylogeny -- character transitions and support.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80). Characters 9, 27, 39, 45 - 47, 49, and 51 are mapped under ACCTRAN optimization; all others are unambiguously optimized. Black squares indicate non-homoplasious character state changes, whereas white squares indicate homoplasious character state changes. The numbers above and below the squares represent character numbers and states, respectively. Bremer support (upper value) and relative fit difference (lower value) values can be found at the left ends of the branches. A ``*'' symbol at the right end of a branch indicates Bootstrap support greater than 0.95.}
	\label{fig:tree1}
\end{figure}

%phylogeny
\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[height=0.85\textwidth]{figure38.png}
	\end{sideways}
	\caption{\textbf{Preferred phylogeny -- clade concept labels.} Topology and species-level taxonomic concept labels as in Fig.~\ref{fig:tree1}. Clade concept labels, numbered 1-20, are consistently generated by using the alphabetically first epithet in each of the bifurcating sister clades. This method safeguards the clade concept labels against changes due simply to reorientation of leaves. Bold-font square brackets indicate new [JF2018] labels. See also \textbf{\nameref{sec:alignments}}.}
	\label{fig:tree2}
\end{figure}
\end{document}
